The Three Corridors

### 2015-01-10 msr.tex
update msr.tex

\keywords{Maven Repository, JDepend, Software Bugs.}

@@

>>>>

\keywords{Maven Repository, JDepend, Software Metrics, Chidamber and Kemerer.}

@@

 Maven is a build automation tool used primarily for Java projects, and it is hosted by the Apache Software Foundation\footnote{\url{http://www.apache.org/}}. To describe the software project being built, its dependencies on other libraries, and the build order Maven uses {\sc xml}. The repository contains more than 400,000 {\sc jar}s, in a variety of languages that are all using the {\sc jvm} platform as basis. These languages include Java, Clojure, Groovy, and Scala.

Initially, a snapshot (January 2012) of the Maven repository was downloaded locally. The repository contains various projects and their releases. A project version can be uniquely identified by the following triplet: {\it group id}, {\it artifact id} and {\it version}. The Maven repository contains several versions of each project.

All versions were filtered out and only the latest was kept. For each version in the Maven repository, each binary {\sc jar} file is accompanied by another {\sc jar}, which contains the source code. Table \ref{tbl:oss-size-metrics} presents several size metrics regarding the final version corpus. It included 12,959 projects, with more than 110 million lines of code.
